3D Magnetic modelling of ellipsoidal bodies

### 2017-02-21 manuscript/manuscript.tex
change the position of the depolarization tensor section

By considering $\tilde{\mathbf{r}}$ as a point within the
volume $\vartheta$ of the ellipsoid and using the Maxwell's postulate 
about the uniformity of the magnetic field $\mathbf{H}(\mathbf{r})$ 
inside ellipsoidal bodies, we can use Eq. \ref{eq:H-tilde}
for defining the resultant uniform magnetic field $\tilde{\mathbf{H}}^{\dagger}$
inside the ellipsoidal body as follows:
\begin{equation}
\tilde{\mathbf{H}}^{\dagger} = 
\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \: ,
\label{eq:Hi-tilde}
\end{equation}
where $\mathbf{I}$ is the identity matrix and 
$\tilde{\mathbf{N}}^{\dagger}$ is a diagonal matrix
representing the transformed depolarization tensor 
evaluated within the volume $\vartheta$ of the ellipsoidal body.
For a given ellipsoid, the elements $\tilde{n}^{\dagger}_{ii}$, 
$i = 1, 2, 3$, of $\tilde{\mathbf{N}}^{\dagger}$ are constants 
which are expressed in terms of the ellipsoid semi-axes.
These elements are presented in detail in a latter section.

Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}^{\dagger}$
(Eq. \ref{eq:Hi-tilde}) by the transformed 
susceptibility tensor $\tilde{\mathbf{K}}$ 
(Eq. \ref{eq:H-tilde}) to obtain
\begin{equation}
\begin{split}
\tilde{\mathbf{M}} 
&= \tilde{\mathbf{K}} 
\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \\
&=  
\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0}
\end{split} \: ,
\label{eq:M-tilde}
\end{equation}
where $\tilde{\mathbf{M}}$
represents the transformed magnetization, as can be easily
verified by using Eqs. \ref{eq:M-KH} and \ref{eq:H-tilde}.
The matrix identity used for obtaining the second line of Eq. 
\ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.
Equation \ref{eq:M-tilde} can be easily generalized for the case in 
which the ellipsoid has also a uniform remanent magnetization
$\tilde{\mathbf{M}}_{R}$. Let us first consider that
the uniform remanent magnetization satisfies the condition
$\tilde{\mathbf{H}}_{A} = \tilde{\mathbf{K}}^{-1} \tilde{\mathbf{M}}_{R}$,
where $\tilde{\mathbf{H}}_{A}$ represents a hypothetical 
uniform ancient field. Then, if we assume that $\tilde{\mathbf{H}}_{0}$,
in Eqs. \ref{eq:Hi-tilde} and \ref{eq:M-tilde},
is in fact the sum of the inducing magnetic field $\tilde{\mathbf{H}}_{0}$ 
and the hypothetical ancient field $\tilde{\mathbf{H}}_{A}$, we obtain the 
following generalized equation
\begin{equation}
\mathbf{M} = \mathbf{\Lambda}
\left(\mathbf{K} \, \mathbf{H}_{0} + \mathbf{M}_{R} \right) \: ,
\label{eq:M-remanence}
\end{equation}
where
\begin{equation}
\mathbf{\Lambda} = \mathbf{V}
\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\mathbf{V}^{\top} \: .
\label{eq:Lambda}
\end{equation}
Despite of the coordinate system transformation represented by the
matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
Eq. \ref{eq:M-remanence} is consistent with that given by
\citet[Eq. ~38]{clark1986}. It shows the combined effect of the
anisotropy of magnetic susceptibility (AMS) and the shape anisotropy.
The AMS is represented by the susceptibility tensor $\mathbf{K}$ 
(Eq. \ref{eq:K}) and reflects the
preferred orientation of the magnetic minerals forming the
body. The susceptibility tensor appears in Eq. \ref{eq:M-remanence},
defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a),
and Eq. \ref{eq:Lambda}, defined in the local coordinate system
(Fig. \ref{fig:orientation-angles}b).
The shape anisotropy is represented, in Eq.\ref{eq:M-remanence} by the
depolarization tensor $\tilde{\mathbf{N}}^{\dagger}$ and
reflects the self-demagnetization associated to the body shape.
Notice that the resultant magnetization $\mathbf{M}$
(Eq. \ref{eq:M-remanence}) does not necessarily have
the same direction as the inducing field $\mathbf{H}_{0}$
(Eq. \ref{eq:H0}).
The angular difference between the resultant magnetization
and the inducing field depends on the combined effect of the
anisotropy of magnetic susceptibility and the shape anisotropy.

By using the concept of vector norm and its corresponding
operator norm \citep{demmel1997, golub2013}, we may use Eq.
\ref{eq:perturbed-M-system} to write the following inequality:
\begin{equation}
\frac{\| \delta \mathbf{M} \|}{\| \mathbf{M} \|} \leq
\| \delta \mathbf{\Lambda}^{-1} \| \: .
\label{eq:perturbed-M-inequality}
\end{equation}
where $\| \delta \mathbf{M} \|$ and $\| \mathbf{M} \|$
denote Euclidean norms (or 2-norms) and the term 
$\| \delta \mathbf{\Lambda}^{-1} \|$ denotes the matrix 2-norm
of $\delta \mathbf{\Lambda}^{-1}$.
By using Eqs. \ref{eq:inverse-Lambda} and \ref{eq:perturbed-inverse-Lambda}
and the orthogonal invariance of the matrix 2-norm
\citep{demmel1997, golub2013}, we define
$\| \delta \mathbf{\Lambda}^{-1} \|$ as follows:
\begin{equation}
\| \delta \mathbf{\Lambda}^{-1} \| = \chi \,
\tilde{n}^{\dagger}_{33} \: ,
\label{eq:norm-perturbed-inverse-Lambda}
\end{equation}
where $\tilde{n}^{\dagger}_{33}$ is defined in the 
following sections, depending on the ellipsoid
type.
It is worth, however, to stress that $\tilde{n}^{\dagger}_{33}$ is
a scalar function of the ellipsoid semi-axes.
In Eq. \ref{eq:perturbed-M-inequality}, the ratio
$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1}$ represents the
\textit{relative error} in the approximated magnetization
$\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx}) with respect
to the true magnetization $\mathbf{M}$ (Eqs. \ref{eq:M-K-isotropic}
and \ref{eq:M-K-isotropic-inverse-Lambda}).

Given a target relative error
$\epsilon = \| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1}$
and an ellipsoid
with given semi-axes, we may use the inequality
represented by Eq. \ref{eq:norm-perturbed-inverse-Lambda}
to define
\begin{equation}
\chi_{max} = \frac{\epsilon}{\tilde{n}^{\dagger}_{33}} \: ,
\label{eq:max-chi}
\end{equation}
which represents the maximum isotropic susceptibility 
that the ellipsoidal body can assume in order o guarantee
a relative error lower than or equal to $\epsilon$.
For isotropic susceptibilities greater than $\chi_{max}$,
there is no guarantee that the relative error in the
approximated magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
with respect to the true magnetization $\mathbf{M}$ 
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda})
is lower than or equal to $\epsilon$. The geoscientific community
has been using $\chi_{max} = 0.1$ SI as a limit value for
neglecting the self-demagnetization and, consequently,
use magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
as a good approximation of the true magnetization $\mathbf{M}$ 
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
Equation \ref{eq:max-chi}, on the other hand, defines $\chi_{max}$ 
as a function of the ellipsoid semi-axes, according to a
user-specified relative error $\epsilon$.

The magnetic field $\Delta \mathbf{H}(\mathbf{r})$ 
produced by an ellipsoid at external points is calculated from 
Eqs. \ref{eq:H-tilde} and \ref{eq:M-remanence} as the difference
between the resultant field $\mathbf{H}(\mathbf{r})$ 
and the inducing field $\mathbf{H}_{0}$:
\begin{equation}
\Delta \mathbf{H}(\mathbf{r}) = 
- \mathbf{V} \tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}}) \, \mathbf{V}^{\top}
\mathbf{M} \: .
\label{eq:delta-H}
\end{equation}
The elements of the transformed depolarization tensor 
$\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used in 
Eq. \ref{eq:delta-H} will be presented in
the following section.

The $\Delta \mathbf{H}(\mathbf{r})$ 
represents the magnetic field produced by a uniformly magnetized 
body located in the crust.
Equation \ref{eq:delta-H} gives the magnetic field
(in \unit{A \, m^{-1}}) produced by an ellipsoid. However,
in geophysics, the most widely used field is the magnetic 
induction (in \unit{nT}). Fortunately, this conversion can
be easily done by multiplying Eq. \ref{eq:delta-H}
by $k_{m}~=~10^{9}~\mu_{0}$, where $\mu_{0}$ represents the
magnetic constant (in \unit{H \, m^{-1}}).
For geophysical applications, it is preferable to
calculate the total-field anomaly produced by the
magnetic sources. This scalar quantity is given by
\citep{blakely1996}:
\begin{equation}
\Delta T(\mathbf{r}) = \| 
\mathbf{B}_{0} + \Delta \mathbf{B}(\mathbf{r}) \|
- \| \mathbf{B}_{0} \| \: ,
\label{eq:delta-T}
\end{equation}
where $\mathbf{B}_{0} = k_{m} \, \mathbf{H}_{0}$
and $\Delta \mathbf{B}(\mathbf{r}) = 
k_{m} \, \Delta \mathbf{H}(\mathbf{r})$,
with $\mathbf{H}_{0}$ and $\Delta \mathbf{H}(\mathbf{r})$ defined,
respectively, by Eqs. \ref{eq:H0} and \ref{eq:delta-H}.
In practical situations, however, 
$\| \mathbf{B}_{0} \| >> \| \Delta \mathbf{B}(\mathbf{r}) \|$
and, consequently, the following approximation is valid \citep{blakely1996}:
\begin{equation}
\Delta T(\mathbf{r}) \approx  
\frac{\mathbf{B}_{0}^{\top} \Delta \mathbf{B}(\mathbf{r})}{\| \mathbf{B}_{0} \|} \: .
\label{eq:delta-T-approx}
\end{equation}

@@

The elements of the transformed depolarization tensor 
$\tilde{\mathbf{N}}^{\dagger}$ used in the previous sections
are calculated according to Eq. \ref{eq:nij-tilde}, with 
$\tilde{f}(\tilde{\mathbf{r}})$ given by 
$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}).
As we have already pointed out, the  
$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}) is a
quadratic function of the spatial coordinates $\tilde{x}$,
$\tilde{y}$ and $\tilde{z}$. Consequently, the 
elements $\tilde{n}^{\dagger}_{ij}$, $i = 1, 2, 3$, 
$j = 1, 2, 3$, of $\tilde{\mathbf{N}}^{\dagger}$ 
do not depend on the elements of the transformed position
vector $\tilde{\mathbf{r}}$ (equation \ref{eq:coord_transformation}). 
Besides, the off-diagonal elements are zero and
the diagonal elements are given by \citep{stoner1945}:
\begin{equation}
\tilde{n}^{\dagger}_{ii} = \frac{abc}{2}
\int_{0}^{\infty} \frac{1}{\left( e_{i}^{2} 
+ u \right) R(u)} \, du \: , \quad i = 1, 2, 3 \: ,
\label{eq:n-tilde-dagger-ii}
\end{equation}
where $R(u)$ is defined by Eq. \ref{eq:R} and
$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$. These elements 
are commonly known as \textit{demagnetizing factors}
and are defined according to the ellipsoid type.
Here, we calculate the demagnetizing factors in the SI
system. Consequently, they satisfies the condition
$\tilde{n}^{\dagger}_{11} + \tilde{n}^{\dagger}_{22} + 
\tilde{n}^{\dagger}_{33} = 1$, independently of the
ellipsoid type.
Notice that, according to Eqs. \ref{eq:H-tilde} 
and \ref{eq:N-tilde-VT-N-V},
\begin{equation}
\mathbf{N}(\mathbf{r}) = 
\mathbf{V} \, \tilde{\mathbf{N}}^{\dagger} \, 
\mathbf{V}^{\top} \: ,
\label{eq:N-V-N-dagger-VT}
\end{equation}
where $\tilde{\mathbf{N}}^{\dagger}$ is a diagonal 
matrix and $\mathbf{V}$ (Eq. \ref{eq:A}) is an orthogonal matrix.
This equation shows that, for the particular case 
in which $\mathbf{r}$ and consequently $\tilde{\mathbf{r}}$
represent a point inside the
volume $\vartheta$ of the ellipsoid, the elements 
$\tilde{n}^{\dagger}_{ii}$ (Eq. \ref{eq:n-tilde-dagger-ii})
of $\tilde{\mathbf{N}}^{\dagger}$ represent the eigenvalues while the 
columns of $\mathbf{V}$ represent the eigenvectors of the 
original depolarization tensor $\mathbf{N}(\mathbf{r})$.

@@

The elements $\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$,
$i = 1, 2, 3$, $j = 1, 2, 3$, of the transformed depolarization tensor 
$\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used to compute
the magnetic field $\Delta \mathbf{H}(\mathbf{r})$ 
(Eq. \ref{eq:delta-H}) and
the total-field anomaly $\Delta T(\mathbf{r})$
(Eqs. \ref{eq:delta-T} and \ref{eq:delta-T-approx}) 
are calculated according to Eq. \ref{eq:nij-tilde}, with 
$\tilde{f}(\tilde{\mathbf{r}})$ given by $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$
(Eq. \ref{eq:fe-tilde}).
By following \citet{clark1986}, the diagonal elements $\tilde{n}^{\ddagger}_{ii}$
and the off-diagonal elements $\tilde{n}^{\ddagger}_{ij}$, $i = 1, 2, 3$,
$j = 1, 2, 3$, are given by
\begin{equation}
\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}}) =
-\frac{abc}{2}
\left( \frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{i} \, \tilde{r}_{i}
+ g_{i} \right)
\label{eq:n-tilde-dagger-ii}
\end{equation}
and
\begin{equation}
\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}}) =
-\frac{abc}{2} \left(
\frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{j} \, \tilde{r}_{j} 
\right) \: ,
\label{eq:n-tilde-dagger-ij}
\end{equation}
where
\begin{equation}
h_{i} = -\frac{1}{\left( e_{i}^{2} + \lambda \right) R(\lambda)} \: ,
\label{eq:hi}
\end{equation}
\begin{equation}
g_{i} = \int_{\lambda}^{\infty} \frac{1}{\left( e_{i}^{2} + u \right) R(u)} du \: ,
\label{eq:gi}
\end{equation}
$e_{1} = a$, $e_{2} = b$, $e_{3} = c$, and 
$\frac{\partial \lambda}{\partial \tilde{r}_{i}}$
is defined in Appendix B (Eq. \ref{eq:dlambda}).
The functions $g_{i}$ (Eq. \ref{eq:gi}) are defined according
to the ellipsoid type.
Notice that the elements $\tilde{n}^{\ddagger}_{ij}$
(Eqs. \ref{eq:n-tilde-dagger-ii} and \ref{eq:n-tilde-dagger-ij}) 
are proportional to the second derivatives of the function
$\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fe-tilde}),
which is harmonic. Consequently, the diagonal elements defined
in Eq. \ref{eq:n-tilde-dagger-ii} satisfies the condition
$\tilde{n}^{\ddagger}_{11}(\tilde{\mathbf{r}}) +
\tilde{n}^{\ddagger}_{22}(\tilde{\mathbf{r}}) +
\tilde{n}^{\ddagger}_{33}(\tilde{\mathbf{r}}) = 0$ for any
point $\tilde{\mathbf{r}}$ outside the ellipsoid, independently
of the ellipsoid type.

@@

For triaxial ellipsoids (e.g., $a > b > c$), the functions
$g_{i}$ (Eq. \ref{eq:gi}) are defined as follows:
\begin{equation}
g_{1} = \frac{2}{\left( a^{2} - b^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
\label{eq:g1-triaxial}
\end{equation}
%\begin{equation}
%g_{2} = \frac{2 \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
%{\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
%\left[ E\left(\kappa, \phi \right) 
%- \frac{\left( b^{2} - c^{2} \right)}{\left( a^{2} - c^{2} \right)}
%F\left(\kappa, \phi \right) 
%- \frac{\kappa^{2} \sin\phi \, \cos\phi}
%{\left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
%\right]
%\label{eq:g2-triaxial}
%\end{equation}
\begin{equation}
g_{2} = \frac{2 \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
{\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
\left\lbrace
E\left(\kappa, \phi \right) 
- \left( \frac{b^{2} - c^{2}}{a^{2} - c^{2}} \right)
F\left(\kappa, \phi \right) -
\frac{a^{2} - b^{2}}{\left( a^{2} - c^{2} \right)^{\frac{1}{2}}} \left[
\frac{c^{2} + \lambda}{\left( a^{2} + \lambda \right)\left( b^{2} + \lambda \right)}
\right]^{\frac{1}{2}} \right\rbrace
\label{eq:g2-triaxial}
\end{equation}
and
%\begin{equation}
%g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
%\left[ \frac{\sin\phi \left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
%{\cos\phi}  - E\left(\kappa, \phi \right) \right]
%\: ,
%\label{eq:g3-triaxial}
%\end{equation}
\begin{equation}
g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
E\left(\kappa, \phi \right) +
\frac{2}{b^{2} - c^{2}}
\left[
\frac{b^{2} + \lambda}{\left( a^{2} + \lambda \right)\left( c^{2} + \lambda \right)}
\right]^{\frac{1}{2}}
\: ,
\label{eq:g3-triaxial}
\end{equation}
where $F(\kappa, \phi)$ and $E(\kappa, \phi)$ are defined by
Eqs. \ref{eq:E-kappa-phi} and \ref{eq:F-kappa-phi}, but with 
$\sin \phi = \sqrt{\left( a^{2} - c^{2} \right)/\left( a^{2} + \lambda \right)}$.
A deduction of these formulas was presented by \citet{tejedor1995}.
Despite the small differences, these formulas can also be found in
\citet{clark1986}.

@@

>>>>

@@

Let $\tilde{\mathbf{N}}^{\dagger}$ be the transformed
depolarization tensor calculated for the case in which
$\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation})
represents a point located outside
the ellipsoidal body. In this case, 
the elements of $\tilde{\mathbf{N}}^{\dagger}$
are calculated according to Eq. \ref{eq:nij-tilde}, 
with $\tilde{f}(\tilde{\mathbf{r}})$ given by 
$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}).
As we have already pointed out, the  
$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}) is a
quadratic function of the spatial coordinates $\tilde{x}$,
$\tilde{y}$ and $\tilde{z}$. Consequently, the 
elements $\tilde{n}^{\dagger}_{ij}$, $i = 1, 2, 3$, 
$j = 1, 2, 3$, of $\tilde{\mathbf{N}}^{\dagger}$ 
do not depend on the elements of the transformed position
vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation}). 
Besides, the off-diagonal elements are zero and
the diagonal elements are given by \citep{stoner1945}:
\begin{equation}
\tilde{n}^{\dagger}_{ii} = \frac{abc}{2}
\int_{0}^{\infty} \frac{1}{\left( e_{i}^{2} 
+ u \right) R(u)} \, du \: , \quad i = 1, 2, 3 \: ,
\label{eq:n-tilde-dagger-ii}
\end{equation}
where $R(u)$ is defined by Eq. \ref{eq:R} and
$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$. These elements 
are commonly known as \textit{demagnetizing factors}
and are defined according to the ellipsoid type.
Here, we calculate the demagnetizing factors in the SI
system. Consequently, they satisfies the condition
$\tilde{n}^{\dagger}_{11} + \tilde{n}^{\dagger}_{22} + 
\tilde{n}^{\dagger}_{33} = 1$, independently of the
ellipsoid type.
It is worth stressing that, according to Eq. \ref{eq:n-tilde-dagger-ii},
the demagnetizing factors $\tilde{n}^{\dagger}_{ii}$ are 
constants defined by the ellipsoid semi-axes $a$, $b$, and $c$.

Notice that, according to Eqs. \ref{eq:H-tilde} 
and \ref{eq:N-tilde-VT-N-V},
\begin{equation}
\mathbf{N}(\mathbf{r}) = 
\mathbf{V} \, \tilde{\mathbf{N}}^{\dagger} \, 
\mathbf{V}^{\top} \: ,
\label{eq:N-V-N-dagger-VT}
\end{equation}
where $\tilde{\mathbf{N}}^{\dagger}$ is a diagonal 
matrix and $\mathbf{V}$ (Eq. \ref{eq:A}) is an orthogonal matrix.
This equation shows that, for the particular case 
in which $\mathbf{r}$ and consequently $\tilde{\mathbf{r}}$
represent a point inside the
volume $\vartheta$ of the ellipsoid, the elements 
$\tilde{n}^{\dagger}_{ii}$
of $\tilde{\mathbf{N}}^{\dagger}$ represent the eigenvalues while the 
columns of $\mathbf{V}$ represent the eigenvectors of the 
original depolarization tensor $\mathbf{N}(\mathbf{r})$.

@@

The elements $\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$,
$i = 1, 2, 3$, $j = 1, 2, 3$, of the transformed depolarization tensor 
$\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ 
are calculated according to Eq. \ref{eq:nij-tilde}, with 
$\tilde{f}(\tilde{\mathbf{r}})$ given by $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$
(Eq. \ref{eq:fe-tilde}).
By following \citet{clark1986}, the diagonal elements 
$\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}})$
and the off-diagonal elements 
$\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$, $i = 1, 2, 3$,
$j = 1, 2, 3$, are given by
\begin{equation}
\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}}) =
-\frac{abc}{2}
\left( \frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{i} \, \tilde{r}_{i}
+ g_{i} \right)
\label{eq:n-tilde-ddagger-ii}
\end{equation}
and
\begin{equation}
\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}}) =
-\frac{abc}{2} \left(
\frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{j} \, \tilde{r}_{j} 
\right) \: ,
\label{eq:n-tilde-ddagger-ij}
\end{equation}
where
\begin{equation}
h_{i} = -\frac{1}{\left( e_{i}^{2} + \lambda \right) R(\lambda)} \: ,
\label{eq:hi}
\end{equation}
\begin{equation}
g_{i} = \int_{\lambda}^{\infty} \frac{1}{\left( e_{i}^{2} + u \right) R(u)} du \: ,
\label{eq:gi}
\end{equation}
$e_{1} = a$, $e_{2} = b$, $e_{3} = c$, and 
$\frac{\partial \lambda}{\partial \tilde{r}_{i}}$
is defined in Appendix B (Eq. \ref{eq:dlambda}).
The functions $g_{i}$ (Eq. \ref{eq:gi}) are defined according
to the ellipsoid type.
Notice that the elements $\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}})$
(Eq. \ref{eq:n-tilde-ddagger-ii}) and 
$\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$
(Eq. \ref{eq:n-tilde-ddagger-ij}) 
are proportional to the second derivatives of the function
$\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fe-tilde}),
which is harmonic. Consequently, the diagonal elements 
$\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}})$ satisfy the condition
$\tilde{n}^{\ddagger}_{11}(\tilde{\mathbf{r}}) +
\tilde{n}^{\ddagger}_{22}(\tilde{\mathbf{r}}) +
\tilde{n}^{\ddagger}_{33}(\tilde{\mathbf{r}}) = 0$ for any
point $\tilde{\mathbf{r}}$ outside the ellipsoid, independently
of the ellipsoid type.

@@

For triaxial ellipsoids (e.g., $a > b > c$), the functions
$g_{i}$ (Eq. \ref{eq:gi}) are defined as follows:
\begin{equation}
g_{1} = \frac{2}{\left( a^{2} - b^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
\label{eq:g1-triaxial}
\end{equation}
%\begin{equation}
%g_{2} = \frac{2 \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
%{\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
%\left[ E\left(\kappa, \phi \right) 
%- \frac{\left( b^{2} - c^{2} \right)}{\left( a^{2} - c^{2} \right)}
%F\left(\kappa, \phi \right) 
%- \frac{\kappa^{2} \sin\phi \, \cos\phi}
%{\left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
%\right]
%\label{eq:g2-triaxial}
%\end{equation}
\begin{equation}
g_{2} = \frac{2 \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
{\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
\left\lbrace
E\left(\kappa, \phi \right) 
- \left( \frac{b^{2} - c^{2}}{a^{2} - c^{2}} \right)
F\left(\kappa, \phi \right) -
\frac{a^{2} - b^{2}}{\left( a^{2} - c^{2} \right)^{\frac{1}{2}}} \left[
\frac{c^{2} + \lambda}{\left( a^{2} + \lambda \right)\left( b^{2} + \lambda \right)}
\right]^{\frac{1}{2}} \right\rbrace
\label{eq:g2-triaxial}
\end{equation}
and
%\begin{equation}
%g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
%\left[ \frac{\sin\phi \left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
%{\cos\phi}  - E\left(\kappa, \phi \right) \right]
%\: ,
%\label{eq:g3-triaxial}
%\end{equation}
\begin{equation}
g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
E\left(\kappa, \phi \right) +
\frac{2}{b^{2} - c^{2}}
\left[
\frac{b^{2} + \lambda}{\left( a^{2} + \lambda \right)\left( c^{2} + \lambda \right)}
\right]^{\frac{1}{2}}
\: ,
\label{eq:g3-triaxial}
\end{equation}
where $F(\kappa, \phi)$ and $E(\kappa, \phi)$ are defined by
Eqs. \ref{eq:E-kappa-phi} and \ref{eq:F-kappa-phi}, but with 
$\sin \phi = \sqrt{\left( a^{2} - c^{2} \right)/\left( a^{2} + \lambda \right)}$.
A detailed deduction of these formulas was presented by \citet{tejedor1995}.
Similar formulas can also be found in \citet{clark1986}.

@@

By considering $\tilde{\mathbf{r}}$ as a point within the
volume $\vartheta$ of the ellipsoid and using the Maxwell's postulate 
about the uniformity of the magnetic field $\mathbf{H}(\mathbf{r})$ 
inside ellipsoidal bodies, we can use Eq. \ref{eq:H-tilde}
for defining the resultant uniform magnetic field $\tilde{\mathbf{H}}^{\dagger}$
inside the ellipsoidal body as follows:
\begin{equation}
\tilde{\mathbf{H}}^{\dagger} = 
\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \: ,
\label{eq:Hi-tilde}
\end{equation}
where $\mathbf{I}$ is the identity matrix and 
$\tilde{\mathbf{N}}^{\dagger}$ is defined in the
previous section.

Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}^{\dagger}$
(Eq. \ref{eq:Hi-tilde}) by the transformed 
susceptibility tensor $\tilde{\mathbf{K}}$ 
(Eq. \ref{eq:H-tilde}) to obtain
\begin{equation}
\begin{split}
\tilde{\mathbf{M}} 
&= \tilde{\mathbf{K}} 
\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \\
&=  
\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0}
\end{split} \: ,
\label{eq:M-tilde}
\end{equation}
where $\tilde{\mathbf{M}}$
represents the transformed magnetization, as can be easily
verified by using Eqs. \ref{eq:M-KH} and \ref{eq:H-tilde}.
The matrix identity used for obtaining the second line of Eq. 
\ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.
Equation \ref{eq:M-tilde} can be easily generalized for the case in 
which the ellipsoid has also a uniform remanent magnetization
$\tilde{\mathbf{M}}_{R}$. Let us first consider that
the uniform remanent magnetization satisfies the condition
$\tilde{\mathbf{H}}_{A} = \tilde{\mathbf{K}}^{-1} \tilde{\mathbf{M}}_{R}$,
where $\tilde{\mathbf{H}}_{A}$ represents a hypothetical 
uniform ancient field. Then, if we assume that $\tilde{\mathbf{H}}_{0}$,
in Eqs. \ref{eq:Hi-tilde} and \ref{eq:M-tilde},
is in fact the sum of the inducing magnetic field $\tilde{\mathbf{H}}_{0}$ 
and the hypothetical ancient field $\tilde{\mathbf{H}}_{A}$, we obtain the 
following generalized equation
\begin{equation}
\mathbf{M} = \mathbf{\Lambda}
\left(\mathbf{K} \, \mathbf{H}_{0} + \mathbf{M}_{R} \right) \: ,
\label{eq:M-remanence}
\end{equation}
where
\begin{equation}
\mathbf{\Lambda} = \mathbf{V}
\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\mathbf{V}^{\top} \: .
\label{eq:Lambda}
\end{equation}
Despite of the coordinate system transformation represented by the
matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
Eq. \ref{eq:M-remanence} is consistent with that given by
\citet[Eq. ~38]{clark1986}. It shows the combined effect of the
anisotropy of magnetic susceptibility (AMS) and the shape anisotropy.
The AMS is represented by the susceptibility tensor $\mathbf{K}$ 
(Eq. \ref{eq:K}) and reflects the
preferred orientation of the magnetic minerals forming the
body. The susceptibility tensor appears in Eq. \ref{eq:M-remanence},
defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a),
and Eq. \ref{eq:Lambda}, defined in the local coordinate system
(Fig. \ref{fig:orientation-angles}b).
The shape anisotropy is represented, in Eq. \ref{eq:M-remanence}, by the
depolarization tensor $\tilde{\mathbf{N}}^{\dagger}$ and
reflects the self-demagnetization associated to the body shape.
Notice that the resultant magnetization $\mathbf{M}$
(Eq. \ref{eq:M-remanence}) does not necessarily have
the same direction as the inducing field $\mathbf{H}_{0}$
(Eq. \ref{eq:H0}).
The angular difference between the resultant magnetization
and the inducing field depends on the combined effect of the
anisotropy of magnetic susceptibility and the shape anisotropy.
